---
title: "1-explore"
author: "bernard-liew"
date: "2021-03-29"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Package

```{r}
# Helper
library (tidyverse)
library (skimr)
library (DataExplorer)
library (janitor)
library (rsample)

# Import
library (rio)

# Missing
library (VIM)
library (naniar)
library (mice)
library (NADIA)
```

Model for Improvement of neckpain: filter by VAS_neckpain_0 > 1.5 AND 0 missing values for all the obseravtions who entered into the full model.

Model for Improvement of armpain: filter by VAS_armpain_0 > 1.5  AND 0 missing values for all the obseravtions who entered into the full model. 

Model for Improvement of disability: filter by disability_0 >= 7  AND 0 missing values for all the obseravtions who entered into the full model. 


# Import

```{r}
df <- import ("data/neck_pain_database_3001.xlsx", sheet = "DATA")
keys <- import ("data/neck_pain_database_3001.xlsx", sheet = "LEGEND")
```

# Tidy

## Convert factors

```{r}
var_as_factors <- keys[["Type of variable"]] == "Factor"

df <- df %>%
  mutate_if (var_as_factors, ~.x %>% 
            as.character() %>% as.factor()) %>% 
  rename (imp_np = improvem_NECKpain,
          imp_ap = improvem_ARMpain,
          imp_dis = improvem_DISAB)

```


## Explore data

```{r}
skim (df)

table (df$improvem_NECKpain, df$improvem_ARMpain, df$improvem_DISAB)

```

```{r}
visdat::vis_dat(df, sort_type = TRUE)
visdat::vis_miss(df, cluster = TRUE)
```


## Missingness

```{r}
aggr(df)

barMiss(df %>%
             select (imp_np, imp_dis))

spineMiss(df %>%
             select (imp_np, imp_dis))

spineMiss(df %>%
             select (imp_np, imp_ap))
```

```{r}
df <- df %>%
  select (-c(diagn_EMG, diagn_CT))

set.seed(123)

# Save the split information for an 80/20 split of the data
df_split <- initial_split(df, prop = 0.80, strata = imp_np)
df_split

train <- training(df_split)
test  <-  testing(df_split)

```

```{r}
train_impute <- mice (train)

train2 <- complete (train_impute)
test_impute <- mice.reuse(train_impute,
                          test)
test2 <- test_impute[[1]]

dat <- list (data = df,
             train = train2,
             test = test2)
```


## Save 

```{r}
saveRDS(dat,
        "output/df.RDS")
```

