---
title: "1-explore"
author: "bernard-liew"
date: "2021-03-29"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Package

```{r, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```


```{r}
# Helper
library (tidyverse)
library (skimr)
library (DataExplorer)
library (janitor)
library (rsample)

# Import
library (rio)

# Missing
library (VIM)
library (naniar)
library (mice)
library (NADIA)

# Plot 
library (cowplot)

# Word

library (flextable)
library (officer)

# Summary
library (qwraps2)

meanNsd_transform <- function (x) {
  
  m <- round (as.numeric (x[1]), 2)
  s <- round (as.numeric (x[2]), 2)

      m_s <- paste0(m, "(", s, ")")
  
    return (m_s)
}
```

Model for Improvement of neckpain: filter by VAS_neckpain_0 > 1.5 AND 0 missing values for all the obseravtions who entered into the full model.

Model for Improvement of armpain: filter by VAS_armpain_0 > 1.5  AND 0 missing values for all the obseravtions who entered into the full model. 

Model for Improvement of disability: filter by disability_0 >= 7  AND 0 missing values for all the obseravtions who entered into the full model. 


# Import

```{r}
df <- import ("data/neck_pain_database_3001.xlsx", sheet = "DATA")
keys <- import ("data/neck_pain_database_3001.xlsx", sheet = "LEGEND")
```

# Tidy

## Convert factors

```{r}
var_as_factors <- keys[["Type of variable"]] == "Factor"

df <- df %>%
  mutate_if (var_as_factors, ~.x %>% 
            as.character() %>% as.factor()) %>% 
  rename (imp_np = improvem_NECKpain,
          imp_ap = improvem_ARMpain,
          imp_dis = improvem_DISAB)

```


## Explore data

```{r}
skim (df)

table (df$improvem_NECKpain, df$improvem_ARMpain, df$improvem_DISAB)

```

```{r}
visdat::vis_dat(df, sort_type = TRUE)
visdat::vis_miss(df, cluster = TRUE)
```


## Missingness

```{r}
aggr(df)

barMiss(df %>%
             select (imp_np, imp_dis))

spineMiss(df %>%
             select (imp_np, imp_dis))

spineMiss(df %>%
             select (imp_np, imp_ap))
```

```{r}
np <- df %>% 
  select (-c(imp_ap, imp_dis)) %>%
  purrr::discard(~sum(is.na(.x))/length(.x)* 100 >= 50) %>%
  rename (outcome = imp_np)

ap <- df %>% 
  select (-c(imp_np, imp_dis)) %>%
  purrr::discard(~sum(is.na(.x))/length(.x)* 100 >= 50)%>%
  rename (outcome = imp_ap)

dis <- df %>% 
  select (-c(imp_np, imp_ap)) %>%
  purrr::discard(~sum(is.na(.x))/length(.x)* 100 >= 60)%>%
  rename (outcome = imp_dis)

df_list <- list (np = vector ("list"),
                 ap = vector ("list"),
                 dis = vector ("list"))

df_list$np$orig <- np
df_list$ap$orig <- ap
df_list$dis$orig <- dis
```



```{r}

for (n in seq_along (df_list)) {
  set.seed(123)
  
  df_split <- initial_split(df_list[[n]]$orig, prop = 0.80, strata = outcome)
  train <- training(df_split)
  test  <-  testing(df_split)
  
  df_list[[n]]$train <- train
  df_list[[n]]$test <- test
}



# Save the split information for an 80/20 split of the data


```

```{r}

for (n in seq_along (df_list)) {
  
  train_impute <- mice (df_list[[n]]$train)
  df_list[[n]]$train_imp <- complete (train_impute)
  
  test_impute <- mice.reuse(train_impute,
                           df_list[[n]]$test)

  df_list[[n]]$test_imp <- test_impute[[1]]
}

# train_impute <- mice (train)
# 
# train2 <- complete (train_impute)
# test_impute <- mice.reuse(train_impute,
#                           test)
# test2 <- test_impute[[1]]
# 
dat <- list (data = df,
             df_list = df_list)
```


## Save 

```{r}
saveRDS(dat,
        "output/df.RDS")
```

## Export descriptive data

```{r}
df_desc <- bind_cols (df[,c(2:4)], df[names (df) %in% names (ap)]) %>%
  select (-ID)
```

### Missing graph

```{r}
f <- plot_missing (df_desc) +
  theme_cowplot()

ggsave ("sm_plot_1.png",
        f,
        device = "png",
        path = "manuscript/",
        units = "in",
        width = 10,
        height = 6,
        dpi = 200)
```

### Descriptives

```{r}

table1 <- tableby(~., 
                  data = df_desc,
                  control=tableby.control(digits=2, digits.p = 3)) %>%
  as.data.frame() %>%
  filter (!term %in% c("Nmiss", "range"))%>%
  select (-c(group.term:term, variable.type, Overall)) 
  
table1 <- table1 %>%
  mutate (Total = map (Total, meanNsd_transform)) %>%
  mutate (Total = ifelse (Total == "NA(NA)", "", Total))


label_names <- c("Neck pain improvement", "No", "Yes",
                 "Arm pain improvement", "No", "Yes",
                 "Disability improvement", "No", "Yes",
                 "Sex", "Male", "Female",
                 "Age (years)", "Mean (SD)",
                 "Employment", "Not applicable", "Not working", "Working",
                 "Pain duration (days)", "Mean(SD)",
                 "Time since first episode (years)", "<1", "1-5", "5-10", ">10",
                 "Chronicity", "Acute", "Chronic",
                 "Baseline neck pain", "Mean(SD)",
                 "Baseline arm pain", "Mean(SD)",
                 "Baseline disability", "Mean(SD)",
                 "Xray diagnosis", "No", "Yes",
                 "MRI diagnosis", "No", "Yes",
                 "Imaging findings of disc degeneration", "No", "Yes",
                 "Imaging findings of facet degeneration", "No", "Yes",
                 "Imaging findings of scoliosis", "No", "Yes",
                 "Imaging findings of spinal stenosis", "No", "Yes",
                 "Imaging findings of disc protrusion", "No", "Yes",
                 "Imaging findings of disc herniation", "No", "Yes",
                 "Clincal diagnosis", "Disc protrusion/herniation", "Spinal stenosis", "Non-specific",
                 "Pharmacological:analgesics", "No", "Yes",
                 "Pharmacological:NSAIDS", "No", "Yes",
                 "Pharmacological:steroids", "No", "Yes",
                 "Pharmacological:muscle relaxants", "No", "Yes",
                 "Pharmacological:opioids", "No", "Yes",
                 "Pharmacological:other", "No", "Yes",
                 "Non-pharmacological treatment", "No", "Yes",
                 "Neruo-reflexotherapy", "No", "Yes"
                 )

table1$label <- label_names

table1 <- table1 %>%
  rename (Variable = label)

my_path <- paste0("manuscript/table_2_", 
                  "descriptive",
                  ".docx")

ft <- flextable(table1) %>%
  autofit()

my_doc <- read_docx()  %>% 
  body_add_flextable(ft) 

print (my_doc, target = my_path)
```

