---
title: "5-results"
author: "Bernard"
date: "2021-06-29"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Load package

```{r}
# Helper
library (tidyverse)
library (cowplot)
# ML
library (mlr3)
library (mlr3learners)
library (mlr3tuning)
library (mlr3viz)
library (mlr3fselect)
library (mlr3pipelines)
library (mlr3hyperband)

# Word
library (flextable)
library (officer)
```

# Create tasks

```{r}
dat <- readRDS("output/df.RDS") 

# Neck pain
train <- dat$df_list$np$train_imp
test <- dat$df_list$np$test_imp
comb <- bind_rows(train, test)
train_id <- 1: nrow (train)
test_id <- (nrow (train) + 1): nrow (comb)
# Set training task
task_np <- TaskClassif$new (id = "neckpain", backend = comb, target = "outcome")
task_np$set_col_roles("ID", roles = "name")

# Arm pain
train <- dat$df_list$ap$train_imp
test <- dat$df_list$ap$test_imp
comb <- bind_rows(train, test)
train_id <- 1: nrow (train)
test_id <- (nrow (train) + 1): nrow (comb)
# Set training task
task_ap <- TaskClassif$new (id = "armpain", backend = comb, target = "outcome")
task_ap$set_col_roles("ID", roles = "name")

# NDI

train <- dat$df_list$dis$train_imp
test <- dat$df_list$dis$test_imp
comb <- bind_rows(train, test)
train_id <- 1: nrow (train)
test_id <- (nrow (train) + 1): nrow (comb)
# Set training task
task_dis <- TaskClassif$new (id = "disability", backend = comb, target = "outcome")
task_dis$set_col_roles("ID", roles = "name")

measures <- list (msr("classif.auc"), 
                  msr("classif.acc"),
                  msr("classif.tpr"),
                  msr("classif.fpr"),
                  msr("classif.fnr"),
                  msr("classif.tnr"))

```

## Set labels

```{r}
ynames <- c("Area under Curve", "Accuracy", "True positive", 
            "False positive", "False negative", "True negative")

perf <- c("Auc", "Acc", "Tpr",
          "Fpr", "Fnr", "Tnr")

mod_names <- c("Logistic","KKNN","Xgboost", "Lasso", "RF", "Nnet", "SVM")

colz <- c("#030303", "#0000FF", "#EE0000", "#00CD00", "#EE9A00", "#912CEE", "#8B4726")
```


# Neck pain

## Internal validation

```{r}
m_list <- readRDS("output/np_result.RDS")

bmr1 <- as_benchmark_result(m_list$rsmp_list$rr_logreg)
bmr2 <- as_benchmark_result(m_list$rsmp_list$rr_kknn)
bmr3 <- as_benchmark_result(m_list$rsmp_list$rr_xgb)
bmr4 <- as_benchmark_result(m_list$rsmp_list$rr_lasso)
bmr5 <- as_benchmark_result(m_list$rsmp_list$rr_rf)
bmr6 <- as_benchmark_result(m_list$rsmp_list$rr_net)
bmr7 <- as_benchmark_result(m_list$rsmp_list$rr_svm)


bmr1$
  combine(bmr2)$
  combine (bmr3)$
  combine (bmr4)$
  combine (bmr5)$
  combine (bmr6)$
  combine (bmr7)

bmr1 

```

### Plot results

```{r}

plot_list <- vector ("list", length (measures))

for (n in seq_along(measures)) {
  
  plot_list[[n]] <- autoplot(bmr1, measure = measures[[n]]) + 
                      theme_cowplot() + 
                      scale_x_discrete(labels = mod_names) +
                      ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) + 
                      ylab (ynames[n])
  
} 

plot_grid(
  plotlist = plot_list,
  align="hv"
)

inner1 = plot_list %>%
  map ("data") %>%
  reduce (inner_join, by = c("nr", "task_id", "learner_id", "resampling_id")) %>%
  pivot_longer(cols = matches ("classif"),
               names_to = "Measure",
               values_to = "Performance") %>%
  mutate (Measure = str_remove (Measure, "classif.") %>%
            factor (levels = c("auc", "acc", "tpr", "fpr", "fnr", "tnr"), labels = ynames)) %>%
  mutate (models = ifelse (grepl ("kknn", learner_id),
                    "Knn", ifelse (grepl ("xgb", learner_id),
                    "Xgboost", ifelse (grepl ("lasso", learner_id),
                    "Lasso", ifelse (grepl ("net", learner_id),
                    "Nnet", ifelse (grepl ("rf", learner_id),
                    "Random forest", ifelse (grepl ("svm", learner_id),
                    "SVM", "Logistic")))))))

ggplot (data = inner1) +
  geom_boxplot(aes (x = models, y = Performance)) +
  facet_wrap(~ Measure, scales = "free") + 
  theme_cowplot() + 
  scale_x_discrete(labels = mod_names) +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1))



```


## External validation

```{r}
pred_list <- vector ("list", length (m_list$model_list))
tune_list <- vector ("list", length (m_list$model_list))

for (n in seq_along(m_list$model_list)) {
  
  m <- m_list$model_list[[n]]
  p <- m$predict(task_np, row_ids = test_id)
  pred_list[[n]] <- p$score (measures)
  tune_list[[n]] <- m$tuning_result
  
} 

names(pred_list) <- mod_names
names(tune_list) <- mod_names

pred <- pred_list %>%
  bind_rows(.id = "models")

names (pred)[-1] <- perf

```

### Tabularise hyperparameters

```{r}

tune_list[-1] <- map (tune_list[-1], ~ .x %>% select (!matches ("learner|x_domain|classif")))

np <- bind_cols(tune_list) %>%
  pivot_longer(cols = everything (),
               names_to = "hypparm", 
               values_to = "np") %>%
  mutate (models = ifelse (grepl ("kknn", hypparm),
                    "Knn", ifelse (grepl ("xgb", hypparm),
                    "Xgboost", ifelse (grepl ("lasso", hypparm),
                    "Lasso", ifelse (grepl ("net", hypparm),
                    "Nnet", ifelse (grepl ("rf", hypparm),
                    "Random forest", "SVM"))))))
```


### Plot results

```{r}

pred_plot1 <- pred %>%
  mutate (models = factor (models, levels = mod_names)) %>%
  pivot_longer(cols = -models,
               names_to = "Measures",
               values_to = "Performance") %>%
  mutate (Measures = factor (Measures, levels = perf, labels = ynames)) %>%
  ggplot() +
  geom_bar(aes (x = Measures, y = Performance, fill = models), 
           position = "dodge", stat = "identity") +
  scale_fill_manual(values =  colz) + 
  theme_cowplot() +
  theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) 

pred_plot1
  
```


# Arm pain

## Internal validation

```{r}
m_list <- readRDS("output/ap_result.RDS")

bmr1 <- as_benchmark_result(m_list$rsmp_list$rr_logreg)
bmr2 <- as_benchmark_result(m_list$rsmp_list$rr_kknn)
bmr3 <- as_benchmark_result(m_list$rsmp_list$rr_xgb)
bmr4 <- as_benchmark_result(m_list$rsmp_list$rr_lasso)
bmr5 <- as_benchmark_result(m_list$rsmp_list$rr_rf)
bmr6 <- as_benchmark_result(m_list$rsmp_list$rr_net)
bmr7 <- as_benchmark_result(m_list$rsmp_list$rr_svm)


bmr1$
  combine(bmr2)$
  combine (bmr3)$
  combine (bmr4)$
  combine (bmr5)$
  combine (bmr6)$
  combine (bmr7)

bmr1

```

### Plot results

```{r}

plot_list <- vector ("list", length (measures))

for (n in seq_along(measures)) {
  
  plot_list[[n]] <- autoplot(bmr1, measure = measures[[n]]) + 
                      theme_cowplot() + 
                      scale_x_discrete(labels = mod_names) +
                      ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) + 
                      ylab (ynames[n])
  
} 

plot_grid(
  plotlist = plot_list,
  align="hv"
)


inner2 = plot_list %>%
  map ("data") %>%
  reduce (inner_join, by = c("nr", "task_id", "learner_id", "resampling_id")) %>%
  pivot_longer(cols = matches ("classif"),
               names_to = "Measure",
               values_to = "Performance") %>%
  mutate (Measure = str_remove (Measure, "classif.") %>%
            factor (levels = c("auc", "acc", "tpr", "fpr", "fnr", "tnr"), labels = ynames)) %>%
  mutate (models = ifelse (grepl ("kknn", learner_id),
                    "Knn", ifelse (grepl ("xgb", learner_id),
                    "Xgboost", ifelse (grepl ("lasso", learner_id),
                    "Lasso", ifelse (grepl ("net", learner_id),
                    "Nnet", ifelse (grepl ("rf", learner_id),
                    "Random forest", ifelse (grepl ("svm", learner_id),
                    "SVM", "Logistic")))))))

ggplot (data = inner2) +
  geom_boxplot(aes (x = models, y = Performance)) +
  facet_wrap(~ Measure, scales = "free") + 
  theme_cowplot() + 
  scale_x_discrete(labels = mod_names) +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1))


```


## External validation

```{r}
pred_list <- vector ("list", length (m_list$model_list))
tune_list <- vector ("list", length (m_list$model_list))

for (n in seq_along(m_list$model_list)) {
  
  m <- m_list$model_list[[n]]
  p <- m$predict(task_ap, row_ids = test_id)
  pred_list[[n]] <- p$score (measures)
  tune_list[[n]] <- m$tuning_result
} 

names(pred_list) <- mod_names
names(tune_list) <- mod_names

pred <- pred_list %>%
  bind_rows(.id = "models")

names (pred)[-1] <- perf

```


### Tabularise hyperparameters

```{r}

tune_list[-1] <- map (tune_list[-1], ~ .x %>% select (!matches ("learner|x_domain|classif")))

ap <- bind_cols(tune_list) %>%
  pivot_longer(cols = everything (),
               names_to = "hypparm", 
               values_to = "ap") %>%
  mutate (models = ifelse (grepl ("kknn", hypparm),
                    "Knn", ifelse (grepl ("xgb", hypparm),
                    "Xgboost", ifelse (grepl ("lasso", hypparm),
                    "Lasso", ifelse (grepl ("net", hypparm),
                    "Nnet", ifelse (grepl ("rf", hypparm),
                    "Random forest", "SVM"))))))
```

### Plot results

```{r}

pred_plot2 <- pred %>%
  mutate (models = factor (models, levels = mod_names)) %>%
  pivot_longer(cols = -models,
               names_to = "Measures",
               values_to = "Performance") %>%
  mutate (Measures = factor (Measures, levels = perf, labels = ynames)) %>%
  ggplot() +
  geom_bar(aes (x = Measures, y = Performance, fill = models), 
           position = "dodge", stat = "identity") +
  scale_fill_manual(values =  colz) + 
  theme_cowplot() +
  theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) 

pred_plot2
  
  
```


# Disability

## Internal validation

```{r}
m_list <- readRDS("output/dis_result.RDS")

bmr1 <- as_benchmark_result(m_list$rsmp_list$rr_logreg)
bmr2 <- as_benchmark_result(m_list$rsmp_list$rr_kknn)
bmr3 <- as_benchmark_result(m_list$rsmp_list$rr_xgb)
bmr4 <- as_benchmark_result(m_list$rsmp_list$rr_lasso)
bmr5 <- as_benchmark_result(m_list$rsmp_list$rr_rf)
bmr6 <- as_benchmark_result(m_list$rsmp_list$rr_net)
bmr7 <- as_benchmark_result(m_list$rsmp_list$rr_svm)


bmr1$
  combine(bmr2)$
  combine (bmr3)$
  combine (bmr4)$
  combine (bmr5)$
  combine (bmr6)$
  combine (bmr7)

bmr1

```

### Plot results

```{r}

plot_list <- vector ("list", length (measures))

for (n in seq_along(measures)) {
  
  plot_list[[n]] <- autoplot(bmr1, measure = measures[[n]]) + 
                      theme_cowplot() + 
                      scale_x_discrete(labels = mod_names) +
                      ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) + 
                      ylab (ynames[n])
  
} 

plot_grid(
  plotlist = plot_list,
  align="hv"
)


inner3 = plot_list %>%
  map ("data") %>%
  reduce (inner_join, by = c("nr", "task_id", "learner_id", "resampling_id")) %>%
  pivot_longer(cols = matches ("classif"),
               names_to = "Measure",
               values_to = "Performance") %>%
  mutate (Measure = str_remove (Measure, "classif.") %>%
            factor (levels = c("auc", "acc", "tpr", "fpr", "fnr", "tnr"), labels = ynames)) %>%
  mutate (models = ifelse (grepl ("kknn", learner_id),
                    "Knn", ifelse (grepl ("xgb", learner_id),
                    "Xgboost", ifelse (grepl ("lasso", learner_id),
                    "Lasso", ifelse (grepl ("net", learner_id),
                    "Nnet", ifelse (grepl ("rf", learner_id),
                    "Random forest", ifelse (grepl ("svm", learner_id),
                    "SVM", "Logistic")))))))

ggplot (data = inner3) +
  geom_boxplot(aes (x = models, y = Performance)) +
  facet_wrap(~ Measure, scales = "free") + 
  theme_cowplot() + 
  scale_x_discrete(labels = mod_names) +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1))


```


## External validation

```{r}
pred_list <- vector ("list", length (m_list$model_list))
tune_list <- vector ("list", length (m_list$model_list))

for (n in seq_along(m_list$model_list)) {
  
  m <- m_list$model_list[[n]]
  p <- m$predict(task_dis, row_ids = test_id)
  pred_list[[n]] <- p$score (measures)
  tune_list[[n]] <- m$tuning_result
} 

names(pred_list) <- mod_names
names(tune_list) <- mod_names

pred <- pred_list %>%
  bind_rows(.id = "models")

names (pred)[-1] <- perf

```


### Tabularise hyperparameters

```{r}

tune_list[-1] <- map (tune_list[-1], ~ .x %>% select (!matches ("learner|x_domain|classif")))

dis <- bind_cols(tune_list) %>%
  pivot_longer(cols = everything (),
               names_to = "hypparm", 
               values_to = "dis") %>%
  mutate (models = ifelse (grepl ("kknn", hypparm),
                    "Knn", ifelse (grepl ("xgb", hypparm),
                    "Xgboost", ifelse (grepl ("lasso", hypparm),
                    "Lasso", ifelse (grepl ("net", hypparm),
                    "Nnet", ifelse (grepl ("rf", hypparm),
                    "Random forest", "SVM"))))))
```

### Plot results

```{r}


pred_plot3 <- pred %>%
  mutate (models = factor (models, levels = mod_names)) %>%
  pivot_longer(cols = -models,
               names_to = "Measures",
               values_to = "Performance") %>%
  mutate (Measures = factor (Measures, levels = perf, labels = ynames)) %>%
  ggplot() +
  geom_bar(aes (x = Measures, y = Performance, fill = models), 
           position = "dodge", stat = "identity") +
  scale_fill_manual(values =  colz) + 
  theme_cowplot() +
  theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) 

pred_plot3
  
```

# Miscellaneous

```{r, eval = FALSE, include = FALSE}

df_param <- np %>%
  inner_join (ap, by = c("models", "hypparm")) %>%
  inner_join (dis, by = c("models", "hypparm")) %>%
  select (models, hypparm, np, ap, dis) %>%
  mutate_if(is.numeric, round, 3)

# Export to word
my_path <- paste0("manuscript/table_", 
                  "hyperparams",
                  ".docx")

ft <- flextable(df_param ) %>%
  autofit()

my_doc <- read_docx()  %>% 
  body_add_flextable(ft)

print (my_doc, target = my_path)
```


```{r, eval = FALSE, include = FALSE}

inner_plot <- bind_rows (inner1, inner2, inner3) %>%
  mutate(Outcome = factor (task_id, 
                           levels = c("neckpain", "armpain", "disability"), 
                           labels = c("Neck paiin", "Arm pain", "Disability"))) %>%
  mutate (models = factor (models, 
                           levels = c("Logistic", "Knn", "Xgboost", "Lasso", "Random forest", "Nnet", "SVM"))) %>%
  group_by(Outcome, models, Measure) %>%
  summarize (Mean = mean (Performance),
             Sd = sd (Performance))


p <- ggplot (data = inner_plot) +
  geom_point(aes (x = models, y = Mean, color = Outcome), position = position_dodge(width = 0.5)) +
  geom_errorbar(aes (x = models, ymin = Mean - Sd, ymax = Mean + Sd, color = Outcome), 
                position = position_dodge(width = 0.5), width = 0) + 
  facet_wrap(~ Measure, scales = "free") + 
  scale_fill_manual(values =  c("red", "blue", "darkgreen")) + 
  scale_color_manual(values =  c("red", "blue", "darkgreen")) + 
  theme_cowplot() + 
  scale_x_discrete(labels = mod_names) +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) +
  ylab ("Performance") + 
  xlab ("Models")

ggsave (filename = "fig2.png",
        plot = p,
        device = "png",
        path = "manuscript",
        width = 8,
        height = 5,
        units = "in",
        dpi = 150)

inner_plot <- inner_plot %>%
  pivot_wider(names_from = "Measure",
              values_from = c("Mean", "Sd"))

xlsx::write.xlsx2(x = as.data.frame (inner_plot),
                  file = "manuscript/performance_internal.xlsx",
                  row.names = FALSE)

```




```{r, eval = FALSE, include = FALSE}

legend <- get_legend(
  # create some space to the left of the legend
  pred_plot1 + theme(legend.box.margin = margin(0, 0, 0, 12))
)



p1 <- plot_grid(
  pred_plot1 + 
    theme(legend.position="none") + 
    xlab (NULL) + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()),
  pred_plot2 + 
    theme(legend.position="none") + 
    xlab (NULL) + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()),
  pred_plot3 + 
    theme(legend.position="none") ,
  ncol = 1,
  align = "h"
)

p1 <- plot_grid(p1, legend, rel_widths = c(3, .4))


ggsave (filename = "fig3.png",
        plot = p1,
        device = "png",
        path = "manuscript",
        width = 8,
        height = 5,
        units = "in",
        dpi = 150)


pred_plot <- bind_rows(pred_plot1$data,
                       pred_plot2$data,
                       pred_plot3$data) %>%
  mutate (Outcome = rep (c("Neck pain", "Arm pain", "Disability"), each = 42)) %>%
  ungroup () %>%
  pivot_wider(names_from = "Measures",
              values_from = "Performance")

xlsx::write.xlsx2(x = as.data.frame (pred_plot),
                  file = "manuscript/performance_external.xlsx",
                  row.names = FALSE)

```
